Case Study: 16S microbiome data (Papa et al., 2012)

### 2018-03-28 datasets/microbiome/microbiome-baxter.Rmd
Add log(ubiquity) as covariate

otu_result_file <- file.path(resdir, "baxter-otus-results.rds")
otu_bench_file <- file.path(resdir, "baxter-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "baxter-genus-results.rds")
gns_bench_file <- file.path(resdir, "baxter-genus-benchmark.rds")
```

@@

@@

>>>>

otu_result_file <- file.path(resdir, "baxter-otus-results.rds")
otu_bench_file <- file.path(resdir, "baxter-otus-benchmark.rds")
otu_bench_file_log_ubiquity <- file.path(resdir, "baxter-otus-log-ubiquity-benchmark.rds")

gns_result_file <- file.path(resdir, "baxter-genus-results.rds")
gns_bench_file <- file.path(resdir, "baxter-genus-benchmark.rds")
gns_bench_file_log_ubiquity <- file.path(resdir, "baxter-genus-log-ubiquity-benchmark.rds")
```

@@

## Multiple-Testing Correction - log(ubiquity)

Let's use `log(ubiquity)` as our `ind_covariate`.

```{r, baxter-logubi-labelcovariate}
res <- dplyr::mutate(res, ind_covariate = log10(ubiquity))
```

```{r, baxter-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file_log_ubiquity)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = otu_bench_file_log_ubiquity)
} else {
    sb <- readRDS(otu_bench_file_log_ubiquity)
}
```

## Benchmark Metrics - log(ubiquity)

```{r, baxter-logubi-metrics, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, baxter-logubi-plot, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

@@

## Multiple-Testing Correction - log(ubiquity)

Let's use log(`ubiquity`) as our `ind_covariate`.

```{r, baxter-genus-logubi-labelcovariate}
res <- dplyr::mutate(res, ind_covariate = log10(ubiquity))
```

```{r, baxter-genus-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_log_ubiquity)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = gns_bench_file_log_ubiquity)
} else {
    sb <- readRDS(gns_bench_file_log_ubiquity)
}
```

## Benchmark Metrics - log(ubiquity)

```{r, baxter-genus-logubi-metrics, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, baxter-genus-logubi-plot, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

```{r, baxter-genus-logubi-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```

### 2018-03-28 datasets/microbiome/microbiome-papa.Rmd
Add log(ubiquity) as covariate

otu_result_file <- file.path(resdir, "papa-otus-results.rds")
otu_bench_file <- file.path(resdir, "papa-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "papa-genus-results.rds")
gns_bench_file <- file.path(resdir, "papa-genus-benchmark.rds")
```

@@

>>>>

otu_result_file <- file.path(resdir, "papa-otus-results.rds")
otu_bench_file <- file.path(resdir, "papa-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "papa-genus-results.rds")
gns_bench_file <- file.path(resdir, "papa-genus-benchmark.rds")
gns_bench_file_log_ubi <- file.path(resdir, "papa-genus-log-ubiquity-benchmark.rds")
```

@@

## Multiple-Testing Correction - log(ubiquity)

Let's use log10(`ubiquity`) as our `ind_covariate`.

```{r, papa-genus-logubi-labelcovariate}
res <- dplyr::mutate(res, ind_covariate = log10(ubiquity))
```

```{r, papa-genus-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_log_ubi)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ibd_alm_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = gns_bench_file_log_ubi)
} else {
    sb <- readRDS(gns_bench_file_log_ubi)
}
```

## Benchmark Metrics - log(ubiquity)

```{r, papa-genus-logubi-metrics, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, papa-genus-logbi-plot, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

```{r, papa-genus-logubi-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```
